\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
updated section 4.2

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a usability study of a phone advertisement (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

>>>>

\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot). These AOIs are usually based on the hypotheses of the experiment. For example, if in a study with Massive Open Online Courses (MOOCs) (Figure \ref{aoi}) the screen can divided into various lines in the video lecture of the MOOC. Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.
